---
title: "My Presentation"
subtitle: "Subtitle"
author: "Jimmy Cheng"
institute: "CMUH"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: 
      - css/xaringan-themer.css 
      - css/mytheme.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "macros.js"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
xaringanExtra::use_tile_view() #press o
xaringanExtra::use_scribble() #press s
#xaringanthemer::style_mono_accent(base_color = "#43418A")
xaringanthemer::style_solarized_light()
knitr::opts_chunk$set(dpi = 300,        # ensures high resolution images
                      out.height='500px',
                      out.width='700px',
                      fig.align='center',
                      echo = FALSE,     # FALSE: code chunks don't show
                      warning = FALSE,  # FALSE: suppresses warning messages
                      error = FALSE)    # FALSE: suppresses error messages
plot= 'https://upload.wikimedia.org/wikipedia/commons/6/64/Mangekyou_Sharingan_Madara_%28Eternal%29.svg'
```

class: inverse, center, middle
background-image: url(`r plot`)
background-size: contain
## .green[永恆萬花筒寫輪眼 contain]

---
class: bottom, right
background-image: url(`r plot`)
background-size: cover
## .bg-black[.blue[永恆萬花筒寫輪眼 cover]]

---
class: inverse, center, middle
# .bg-red[永恆萬花筒寫輪眼]

----
<br style="line-height: 150px">

.left-col[.center[
<img src=`r plot` style="width: 30%" />
### Label 1
]]

.center-col[
.center[
<img src=`r plot` style="width: 50%" />
### Label 2
]]

.right-col[.center[
<img src=`r plot` style="width: 70%" />
### Label 3
]]

---
<br style='line-height: 200px'>
.center[![:scale 30%](`r plot`)]

---
```{r, echo=FALSE, fig.align='center', dpi=300, out.height='600px'}
knitr::include_graphics(plot)
```

---
class: inverse, center, middle
# *Thanks for Your Attention !*
